First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
add Carmans comments, part A

\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}

@@

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the 
exclusive process of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
$^4$He gas target in front of the CEBAF large acceptance spectrometer 
(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
electromagnetic calorimeter at forward angles, a specially designed radial 
time projection chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than that observed on the free proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
model-independent way, the real and imaginary parts of its unique 
Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. The 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but contamination from incoherent processes could influence the measurement 
significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
can however guaranty that the nucleus remains intact.

@@

The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
measure DVCS observables on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The 5 T solenoid magnet acts as a guiding field for the 
low-energy M\o{}ller electrons, that are absorbed in a  
heavy shield placed around the beam line.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging 300 MeV/c. CLAS cannot detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC) to complement CLAS. The 
RTPC is a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC is the target, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
6~atm of gaseous $^4$He. The experiment (E08-024) collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei by utilizing elastic scattering 
$e^4$He$\to e^\prime$$^4$He with a 1.2~GeV electron beam.

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, light yield, time, and energy obtained from 
the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
are identified in the RTPC using time and energy-loss cuts for tracks in the 
fiducial region~\cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the 
target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. These
are caused by accidental coincidences of soft photons that do not affect 
directly our measurement. We consider only the most energetic photon of an 
event as a DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity observables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements, and their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
The distributions are shown as a function of Bjorken variable $x_B$ (left) 
and as a function of squared-momentum transfer $-t$ (right).}
\label{fig:kin-coverage}
\end{figure}

We identified two main backgrounds to our measurement, accidental coincidences 
and exclusive coherent
$\pi^0$ production. The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this contamination, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
We used this generator together with a GEANT3 simulation of our 
detectors to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data. Depending on the kinematics, we found contaminations of 
2 to 4\%.

@@

There is an additional process contributing to the same final state as the 
DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends of the target form factors, while the DVCS amplitude 
depends on GPDs. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
explicit expressions of the kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

@@

\begin{figure*}[tb]
\includegraphics[width=17cm]{figs/coherent-ALU_90_2.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, the curves represent the theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure*}

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
The black-dashed curves are calculations from the same 
model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
blue long-dashed curve on the top-right plot is from
the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Fig.~\ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, this result is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
measurement is not at a sufficient level to discriminate between the models, 
these results demonstrate the possibility of extracting the CFF of a spin 0 
target directly from a $A_{LU}$ measurement.

>>>>

\title{First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei}

@@

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the 
exclusive process of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
$^4$He gas target in front of the CEBAF Large Acceptance Spectrometer 
(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
electromagnetic calorimeter at forward angles, a specially designed radial 
time projection chamber was used to detect the recoiling $^4$He
nuclei and to ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than those observed on the free proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
model-independent way, the real and imaginary parts of its unique 
Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu$ is the energy of the virtual photon, and 
$M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. The 
measurement was performed on a large set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
but contamination from incoherent processes could influence the measurement 
significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
can however guarantee that the nucleus remains intact.

@@

The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab has been
previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
measure DVCS observables on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
extended the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The 5 T solenoid magnet acted as a guiding field for the 
low-energy M\o{}ller electrons that were absorbed in a  
heavy shield placed around the beam line.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging 300 MeV/c. CLAS could not detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC) to complement CLAS. The 
RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC was the target, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
6~atm of gaseous $^4$He. The experiment (E08-024) collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei by utilizing elastic scattering 
$e^4$He$\to e^\prime$$^4$He with a 1.2~GeV electron beam.

%DVCS selection
To identify coherent DVCS events, we first selected events where one electron, 
one $^4$He, and at least one photon were detected in the final state. Electrons 
were identified using their measured momentum, light yield, time, and energy obtained from 
the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
were identified in the RTPC using time and energy-loss cuts for tracks in the 
fiducial region~\cite{Hattawy:thesis}. In addition, we applied a vertex-matching 
cut to ensure that the 
electron and helium nucleus originated from a common reaction vertex in the 
target cell. The photons were 
detected in either the IC or the CLAS electromagnetic calorimeters. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon were not discarded at this stage. These
were caused by accidental coincidences of soft photons and did not affect 
directly our measurement. We consider only the most energetic photon of an 
event as a DVCS photon candidate.
This prescription however slightly increased the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurred at the partonic level and that the DVCS handbag 
diagram was dominant, we selected events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction was optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity observables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
rejected events where a $\pi^0$ was identified by the invariant mass reconstruction of 
two photons. About 3200 events passed these requirements, and their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those that passed all of the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime{^4}$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^2$ after the exclusivity cuts. 
The distributions are shown as a function of Bjorken $x_B$ (left) 
and as a function of the squared-momentum transfer $-t$ (right).}
\label{fig:kin-coverage}
\end{figure}

We identified two main backgrounds to our measurement, accidental coincidences 
and exclusive coherent
$\pi^0$ production. The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with the scattered electron and 
$^4$He originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this contamination, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
We used this generator together with a GEANT3 simulation of our 
detectors to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data. Depending on the kinematics, we found contaminations of 
2 to 4\%.

@@

There is an additional process contributing to the same final state as the 
DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude depends of the target form factors, while the DVCS amplitude 
depends on GPDs. For our kinematics, the cross section of real photon 
electroproduction is dominated by the BH contribution, while the DVCS 
contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
$A_{LU}$. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
explicit expressions of the kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The grey bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation Eq.~(\ref{eq:A_LU-coh}).}
\label{fig:alu}
\end{figure}

@@

\begin{figure*}[tb]
\includegraphics[width=17cm]{figs/coherent-ALU_90_2.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves represent the theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure*}

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as a function of
$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
The black-dashed curves are calculations from the same 
model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
blue long-dashed curve on the top-right plot is from
the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Fig.~\ref{fig:CFF_HA}. The curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Fig.~\ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model-dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
measurement is not at a sufficient level to discriminate between the models, 
these results demonstrate the possibility of extracting the CFF of a spin-0 
target directly from a $A_{LU}$ measurement.
